% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%

\documentclass[runningheads]{llncs}
%
\pagestyle{plain}

%\usepackage{caption}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
%%\usepackage{subfigure}
%\usepackage{url}
\usepackage{multirow}
%\usepackage{listings}
%\usepackage{cite}
\usepackage{array}
%\usepackage{enumerate}
%%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage{xcolor}
%\usepackage{color}




\begin{document}
%
\title{Another Lattice Attack against the wNAF Implementation of ECDSA to Recover More Bits per Signature}


%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
%Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{Princeton University, Princeton NJ 08544, USA \and
%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
%\email{lncs@springer.com}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
%\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%

\begin{abstract}
This paper presents a practical cache side channel attack on ECDSA implementations which use
 the windowed Non-Adjacent-Form (wNAF) representation to compute the scalar multiplication over elliptic curves.
Compared with the existing works,
    our method extracts more information from the side channels,
      which is then  efficiently used to construct lattice attacks for the ECDSA private key recovery.
 First,
  unlike previous works only monitoring the double and add functions of the scalar multiplication in the cache side channel attacks,
   we add an extra monitor on the invert function
    and get a Double-Add-Invert chain through the side channel.
   %and
    %obtain the sign information of the wNAF representation of an ephemeral key through it.
 %we monitor the invert function in the OpenSSL implementation of the scalar multiplication,
  %  in addition to the functions of double and add which are the only ones exploited in the literature.
%By monitoring the invert function,
    %we obtain the signs of the wNAF representation of an ephemeral key.
% Through this improvement, we obtain the extra information about the sign of the wNAF representations the ephemeral key.
Then, we develop effective methods extracting
    $154.2$ bits information of the ephemeral key per signature
    for 256-bit ECDSA from this chain,
    much more than the best known result which extracts $105.8$ bits per signature.
Finally, to efficiently use the extracted information,
    we convert the problem of recovering the private key to the Hidden Number Problem (HNP) and Extended Hidden Number Problem (EHNP) respectively,
 which are solved by lattice reduction algorithms.
We implemented the Flush+Flush method to attack the ECDSA with the secp256k1 curve in OpenSSL 1.1.0h.
The experimental results show that only $2$ signatures are enough to recover the private key,  % is successfully recovered from only $2$ signatures,
    if the side channel is built without any error. %, which is also required in other works and can be achieved with existing cache side channel attacks.
To the best of our knowledge, this work is the first one to obtain and exploit all signs of the wNAF representations
    in the side channel attacks against ECDSA,
     and requires the least number of signatures for ECDSA private key recovery.

\keywords{ECDSA \and windowed Non-Adjacent-Form \and  OpenSSL \and  Lattice Attack \and  Hidden Number Problem \and  Extended Hidden Number Problem \and  Cache Side Channel.}

\end{abstract}


\input{chap/introduction}
\input{chap/preliminary}
\input{chap/ecdsa_attack}
\input{chap/implementation_experiment}
\input{chap/discussions}
%\input{chap/related_work}
\input{chap/conclusion}


%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.

%\begin{acks}
%To Robert, for the bagels and explaining CMYK and color spaces.
%\end{acks}


%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%

 \bibliographystyle{splncs04}
 \bibliography{bib/Reference}


%\appendix
%\input{chap/appendix}

\end{document}

%%
%% End of file `sample-sigconf.tex'.
