\section{Introduction}
\label{sec:intro}

The Elliptic Curve Digital Signature Algorithm (ECDSA)~\cite{Johnson2001,ansi2005} is a digital signature scheme based on the elliptic-curve \hyphenation{crypto-graphy} cryptography (ECC),
    which is widely used in many popular applications, such as TLS \cite{rfc5246}, OpenPGP \cite{openpgp2007}, smart card \cite{smartcard2007}, and Bitcoin \cite{bitcoin2008}.
The core operation of ECDSA is the scalar multiplication of a base point (or generator) over elliptic curves
    by a random nonce (or ephemeral key).
 And its semantical security relies on the computational intractability to find the ephemeral key for
any given pair of a scalar multiplication and a base point, i.e., the elliptic curve
discrete logarithm problem (ECDLP).
% the intractability of the elliptic curve discrete logarithm problem (ECDLP), that is
% the inability to compute the scalar (ephemeral key) given the original (base) and product points.

However, side channel attacks can obtain the information on the ephemeral key, during the scalar multiplication.
As long as some bits of the ephemeral key are leaked,
    the ECDSA private key will be recovered \cite{Nguyen2001,HG2001,Nguyen2002,Nguyen2003}.
%The partial ephemeral key exposure attack was first proposed by
Howgrave-Graham and Smart~\cite{HG2001} theoretically showed that DSA was vulnerable to such
partial ephemeral key exposures in 2001.
%in 2001 to recover the whole DSA private key.
Then, Nguyen and Shparlinski \cite{Nguyen2002} improved this theoretical attack, and extended it from DSA
to ECDSA \cite{Nguyen2003}.
The basic idea is to reduce the problem of private key recovery to  an instance of  Hidden Number Problem (HNP) with the partial knowledge of the ephemeral keys,
 and then reduce it to the Closest Vector Problem (CVP) or the Shortest Vector Problem (SVP) in a lattice.
Instead of HNP, Fan~\cite{Fan2016} translated the problem of private key recovery to the Extended Hidden Number Problem (EHNP)~\cite{ehnp},
and constructed a more efficient lattice attack.
%The Extended Hidden Number Problem (EHNP)~\cite{ehnp}. was introduced as another way to construct the problem to be solved in the lattice to recover the private key using the partial ephemeral key information.

%Bodo Moeller 30-Jul-2002: Beta 3 of OpenSSL 0.9.7 is now available 开始支持OpenSSL 0.9.7

%The cache side channel attack is an efficient way to obtain the partial information of the ephemeral key,
% and various practical attacks are proposed to recover the ECDSA private key with these information.
With the Flush+Reload cache side channels \cite{flushreload}, various practical attacks~\cite{Benger2014,Van2015,Fan2016,Wang2017} are proposed to attack OpenSSL implementation~\cite{openssl} of ECDSA, in which the windowed Non-Adjacent Form (wNAF) implementation is adopted as the default one for scalar multiplication between  version 0.9.7 and 1.1.0h.
Using the side channel attacks, these works~\cite{Benger2014,Van2015,Fan2016,Wang2017} observe the execution of ECDSA, and get the sequence of points additions and doubling (denoted as Double-Add chain) during the generation of an ECDSA signature.
Then, they extract and exploit the different information of the ephemeral key from this chain,
 and translate the problem of recovering the ECDSA private key to the HNP or EHNP, which is solved by lattice reduction algorithms.

 These attacks~\cite{Benger2014,Van2015,Fan2016,Wang2017} obtain the information of the ephemeral key's wNAF representation \emph{only} from the Double-Add chain, from which different numbers of bits are extracted and exploited to construct the lattice attacks for the private key  recovery.
However, the number of bits extracted from each signature reaches a bottleneck.
The method proposed by Fan is believed to extract almost all the available information of the Double-Add chain~\cite{Fan2016}.
This method~\cite{Fan2016} extracts all positions of digits and obtains $105.8$ bits per signature on average, which performs remarkably better than other attacks~\cite{Benger2014,Van2015,Wang2017}.
Benger et al. \cite{Benger2014} extracted the LSBs of the ephemeral keys and obtained  $2$ bits per signature on average.
Van de Pol et al.~\cite{Van2015}  exploited the positions of higher half non-zero digits and obtained on average $47.6$ bits per signature.
%The number of required signatures  is reduced to $4$.
While, Wang et al.~\cite{Wang2017} exploited the positions of two non-zero digits together with the length of the ephemeral key's wNAF representation, which obtained at least $2.99$ bits per signature on average.
Naturally, more bits are obtained,  fewer signatures are required for recovering the ECDSA private key.
For example,  existing methods ~\cite{Fan2016,Benger2014,Van2015,Wang2017} require $4$, $200$, $13$ and $85$ signatures respectively.
%这一部分仍需要修改

%只是对数据分析进行了改进，并没有获得更多的数据
%As analyzed above,
%The analysis on existing attacks~\cite{Benger2014,Van2015,Fan2016,Wang2017} demonstrated that they extract the information of the ephemeral key's wNAF representation, \emph{only} through the Double-Add chain.
%The difference of these works is that different parts of the  ephemeral key's  wNAF representation are used to construct the lattice attacks.
%For example, the least non-zero digit, half non-zero digits, all non-zero digits and two non-zero digits with the total length are exploited from the ``double-add" chain in~\cite{Benger2014,Van2015,Fan2016,Wang2017}, respectively.
%While, no extra information about the ephemeral key is extracted from the side channels.
%以下为原来的内容
%The above works extracted the information in the wNAF representation of the ephemeral key.
%They tried to make better use of the data achieved through the side channels and construct more effective lattice attacks
% to recover the private key.
%They extracted the least non-zero digit \cite{Benger2014}, half non-zero digits \cite{Van2015}, all non-zero digits \cite{Fan2016} or two non-zero digits with the total length~\cite{Wang2017}.
%In summary,
%all information exploited in these attacks are from the ``double-add" chain, and no more extra information about the ephemeral key is extracted from the side channels.
%Although the lattice attacks are different in these works,
%     no effort and improvement have been made to achieve and exploit more information.
In this paper, we propose a more efficient attack against the wNAF implementation of ECDSA,
which obtains  $154.2$ bits per signature for 256-bit ECDSA on average and requires only $2$ signatures to recover the ECDSA private key.
To achieve this, we obtain more information from the side channel than the methods based on the Double-Add chain~\cite{Benger2014,Van2015,Fan2016,Wang2017},
 and then translate the problem of ECDSA private key recovery to HNP and EHNP with the extracted information respectively, attempting to fully utilize these information.


First, we learn from  Allan's work~\cite{Allan2016} to monitor the invert function in addition to points addition and doubling functions in the cache side channel, and and then construct a Double-Add-Invert chain instead of the Double-Add chain~\cite{Benger2014,Van2015,Fan2016,Wang2017}.
The invert function of the ECDSA implementation in OpenSSL is invoked only when the sign of current non-zero digit of the ephemeral key's wNAF representation is opposite to the previous one in the scalar multiplication.
Therefore, in addition to the positions of all non-zero digits in the ephemeral key's wNAF representation, we can extract the signs of the non-zero digits by monitoring the invert function.

%the length of the consecutive bits used to construct the HNP instance should be larger than 7
Then, with these extracted information, we construct the HNP and EHNP instances respectively, attempting to fully utilize the extracted information.
To construct the HNP instance,
we first recover the consecutive bits at the position of each non-zero digit of the ephemeral key based on the Double-Add-Invert chain,
 and then use these bits to construct an HNP instance for the ECDSA private key recovery.
However, as analyzed in Section~\ref{data_proc2}, the construction of the HNP instance requires the length of the consecutive bits to be larger than $7$,
 and therefore needs more signatures, i.e., $248$.
To improve the utilizing method,
we construct an EHNP \cite{ehnp} instance to recover the ECDSA private key,
 which is further transformed to the approximate SVP in some suitable lattice.
Compared to~\cite{Fan2016}, the constructed lattice is improved with the extra information extracted from the Double-Add-Invert chain.
Therefore, the lattice reduction algorithm to find the target vector becomes easier, and our method only needs $2$ signatures for the 256-bit curve, which  achieves the optimal bound. The details are provided in  Section~\ref{sec:recoverEHNP}.


%We try to not only make better use of the information achieved from side channels,
%  but also to extract different information from the side channels.
%the invert function is another exploitable vulnerability in the implementation of the scalar multiplication.
%This function inverts a number so that the subtraction is replaced by addition and the space storing the precomputed points is reduced by half.
%When computing the scalar multiplication, the invert function is called if the sign of current non-zero digit of the ephemeral key is opposite to the previous one, and the absolute value of this %digit is used to index the precomputed points. Otherwise, the invert function is not called.
%This fact helps us to determine the sign of the non-zero digits of the wNAF representation.
%Therefore, we add a extra monitor to the invert function so that
% we get a Double-Add-Invert chain through the cache side channel and can extract more information about the ephemeral key compared to previous attacks.

%After that, we try to use all the information achieved to recover the ECDSA private key.
%we first recover the consecutive bits at the position of every non-zero digits of the ephemeral key based on the Double-Add-Invert chain
% and construct an HNP instance to  recover the ECDSA private key.
% Due to the length limitation of the consecutive bits, this method needs more signatures than \cite{Van2015}.
%Then,
%we propose a novel method to
%construct an EHNP \cite{ehnp} instance to recover the ECDSA private key by converting it to the SVP problem and solving it with lattice reduction algorithms.
%In the novel method, the short vectors are  much easier to be found by the lattice reduction algorithm comparing to the constructed lattice in \cite{Fan2016}.
%And the signatures needed to recover the ECDSA private key are significantly reduced, which can attain the optimal bound (i.e. 2 for the 256-bit curve).

We applied our attack methods to the secp256k1 curve in OpenSSL 1.1.0h.
We use the Flush+Flush~\cite{gruss2016flush} attack to monitor the functions of double, add and invert, and construct the Double-Add-Invert chain.
From this chain, we successfully determine whether each digit of the ephemeral key's wNAF representation is zero or not,
 and also the signs of the non-zero digits.
 %We extract $153.2$ bits on average per signature for the 256-bit ECDSA.
We extract on average 154.2 bits from
the perfect Double-Add-Invert chain per signature for the 256-bit
elliptic curve.
When using the HNP to recover the ECDSA private key, we need about $248$ signatures to recover the private key with a probability of $1.5\%$.
While using the EHNP, $3$ signatures would be enough to recover the 256-bit ECDSA private key with probability no less than $73\%$,
 and  $2$ signatures with a success probability being not less than $24.3\%$.
%only 3 signatures are needed  to recover the secret key with a high success probability no less than $73\%$.
%And when we have only two signatures, we can recover the secret key with a success probability no less than $24.3\%$.
%Then we use the BKZ \cite{Schnorr1994} algorithm to solve the EHNP instance,
%    and effectively recover the ECDSA private key.
% we only need $2$ signatures to recover the private key with a probability of $3\%$.
This result attains the optimal bound and is the best one as ever known.

%Through the cache side channel, we get the information about the positions and the signs of all non-zero digits of the ephemeral key.
%Compared to previous works, our method obtains more information about the ephemeral key, i.e. the signs of all non-zero digits.
%We extract $153.2$ bits on average per signature for 256-bit ECDSA, which makes only $2$ signatures are enough to recover the ECDSA private key.
%To make better use of the obtained information of the non-zero digits,
% we exploit them to extract sequences of consecutive bits of $k$ and construct the lattice attack.
%We obtain multiple consecutive bits of the ephemeral key by converting the wNAF representation to the binary representation.
%And then, we use these consecutive bits to construct the EHNP instance.
%To the best of our knowledge, it is the first time to obtain and exploit all the
%signs of the wNAF representation in the side channel attacks against ECDSA
%and our attack needs the least number of signatures to recover the ECDSA private key.

%We have improved the attacks against ECDSA in two aspects.
%And
Our contributions are summarized as follows:
\begin{itemize}
  \item
%    We
%    improve the cache side channel attacks by monitoring
%      the invert function. % to obtain the more information of the ephemeral key.
%      It is the first work to extract all signs of the non-zero digits of the ephemeral key in side channel attacks.
    We use the Flush+Flush technique to improve the cache side channel attacks proposed by Allan~\cite{Allan2016} to get higher resolution without using the performance degradation.
  \item
  We present two new lattice attacks to exploit the positions and signs of all non-zero digits in the ephemeral key's wNAF
  representation obtained from the Double-Add-Invert chain.  That is,  we translate the problem of ECDSA private key recovery to the HNP and ENHP respectively.
  Moreover, the attack based on EHNP works better than all known attacks.
% First,   we extract multiple consecutive bits of the ephemeral key by converting the wNAF representation to the binary representation and construct the HNP instance to recover the ECDSA private key.   Second,  we propose a novel method to construct an EHNP instance to recover the ECDSA private key which is better than \cite{Fan2016}.

  \item
    We apply our methods to attack the secp256k1 curve in OpenSSL 1.1.0h. %2018-Mar-27
     Through the cache side channel, $154.2$ bits are obtained per signature  on average.
    The experiments show that only $2$ signatures are enough to recover the private key with a success probability no less than $24.3\%$.
\end{itemize}

The rest of this paper is organized as follows.
Section \ref{sec:background} presents the preliminaries.
Section \ref{sec:attack} shows how to improve the cache side channel to obtain more information.
Section \ref{sec:recoverHNP} and \ref{sec:recoverEHNP} provide how to construct the lattice attacks with HNP and EHNP, respectively.
Section \ref{sec:compare} compares our attacks with existing works.
Section \ref{sec:discussion} contains some extended discussions.
%Section \ref{sec:relatedwork} introduces some related works.
And, Section \ref{sec:conclusion} draws the conclusion.

%ECDSA被广泛应用
%基于椭圆曲线离散对数问题
%算法分析上难以被攻击
%但是在实现上却相对容易发现漏洞
%因此很多人通过侧信道攻击来获取软件实现上的泄露的信息，进行密钥恢复。
%Cache侧信道攻击在近年来得到广泛应用
%
%OpenSSL的实现是应用最广泛的实现。
%其中，对于素域上的椭圆曲线，使用的是wNAF算法实现的标量乘法。
%XX年，提出了对这种方式的的攻击
%XX攻击，使用Flush+Reload攻击获取了多少数据，构造了格攻击
%。。。
%在我们的文章中，我们使用了。。。做了。。。
%达到了。。。
%总的来说，本文的贡献如下：
%1、
%2、
%
%文章的剩余部分这样组织：第二章。。。。

