\section{Preliminaries and Related Works}
\label{sec:background}
In this section, we first present the basic knowledge about the ECDSA and its implementation using the wNAF representation in OpenSSL.
Then, we describe the attack method of the cache side channels.
Also, the hidden number problem and the extended hidden number problem are introduced to utilize the data obtained from cache side channels.
Finally, we provide the related works.

\subsection{The Elliptic Curve Digital Signature Algorithm}
\label{intro_ecdsa}
ECDSA \cite{Johnson2001, ansi2005} is the migration of the Digital Signature Algorithm (DSA) \cite{DSS186} from the multiplicative group of a finite field to the group of points on an elliptic curve.

Let $E$ be an elliptic curve defined over a finite field $\mathbb{F}_{p}$ where $p$ is prime.
$G \in E$ is a fixed point of a large prime order $q$, that is $G$ is the generator of the group of points of order $q$.
These curve and point parameters are publicly known.
The private key of ECDSA is an integer $\alpha$ that satisfies $0 < \alpha < q$,
 and the public key is the point $Q = \alpha G$.
Given a hash function $h$, the ECDSA signature of a message $m$ is computed as follows:
\begin{enumerate}
  \item
    Select a random ephemeral key $0 < k < q$.
  \item
    Compute the point $(x, y) = kG$, and let $r = x$ mod $q$;
    if $r = 0$, then go back to the first step.
  \item
    Compute $s = k^{-1} (h(m) + r\cdot\alpha)$ mod $q$;
    if $s = 0$, then go back to the first step.
\end{enumerate}

The pair $(r, s)$ is the ECDSA signature of the message $m$.
For ECDSA signature, the ephemeral key $k$ must be kept random and secret.
The equation in the third step shows the private key can be computed if $k$ is leaked.
%If some signatures use the same $k$, or the random number generator in use is predictable, attackers can obtain the private key directly. 这个事情，与我们无关；相同k
Even if a portion of $k$ is known, the private key can be recovered by lattice attacks.
Therefore, the scalar multiplication $kG$ becomes the target of most attackers. % who expect to get the information about $k$.

%Given the knowledge of the ephemeral key k and all the
%known information of (s, r,m), the secret key can be easily
%recovered by
%α = r?1(s ・ k ? H(m)) mod q .


\subsection{The Scalar Multiplication using wNAF Representation}
\label{intro_wnaf}
%wnaf 是什么
%K 是有限域， P 是定义在域 K上的椭圆曲线 E(K)上的点，k是一个大整数,根据椭圆曲线上点的加法公式将点P与自身相加 k次, k 称为标量， kP称为椭圆曲线点乘，或标量乘法

Scalar multiplication $kG$ on the elliptic curve means that the point $G$ is added to itself $k$ times,
where $G$ is a point defined on the elliptic curve over the finite field,
 and the scalar $k$ is a big integer.
There are several algorithms to implement the scalar multiplication.
In OpenSSL, scalar multiplication in the prime field is implemented using the wNAF representation \cite{GORDON1998129,Miyaji1997,Koyama1002,Solinas2000} of the scalar $k$.
In wNAF, a number $k$ is represented by a sequence of digits which is either zero or an odd number satisfying $-2^{w} < k_{i} < 2^{w}$,
 where $w$ is the window size. In this representation, any  non-zero digit  is followed by at least $w$ zero digits.
The value of $k$ can be expressed as $k = \sum{2^{i} k_{i}}$.
Algorithm \ref{alg:wnaf} introduces the concrete method for converting a scalar into its wNAF representation.

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

 \begin{algorithm}[t]
        \caption{Conversion to wNAF Representation}
        \label{alg:wnaf}
        \begin{algorithmic}[1]
            \Require Scalar $k$, window size $w$
            \Ensure $k$ in wNAF: $k_0$, $k_1$, $k_2$, ...

            \State $i \gets 0$
            \While{$k > 0$}
                \If {$k$ mod $2 = 1$}
                    \State $k_i \gets k$ mod $2^{w+1}$
                    \If {$k_{i} \geq 2^{w} $}
                        \State $k_{i} \gets k_{i} - 2^{w+1}$
                    \EndIf
                    \State $k \gets k - k_{i}$
                \Else
                    \State $k_{i} \gets 0 $
                \EndIf
                \State $k \gets k/2 $
                \State $i \gets i+1 $
            \EndWhile
        \end{algorithmic}
    \end{algorithm}

%二进制转化成naf
%转化后如何计算标量乘法
For the scalar multiplication using wNAF representation, during the initialization phase,
  a window size $w$ is chosen, and the points $\{\pm G, \pm 3G, ..., \pm(2^{w}-1)G\}$ are precomputed and stored.
Then, for each $k$, after converting it to the wNAF form, the multiplication $kG$ is executed as described in Algorithm \ref{alg:kg}.

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

 \begin{algorithm}[t]
        \caption{Implementation of $kG$ Using wNAF}
        \label{alg:kg}
        \begin{algorithmic}[1]
            \Require Scalar $k$ in wNAF: $k_0$, $k_1$, ..., $k_{l-1}$ and precomputed points $\{\pm G, \pm 3G, ..., \pm(2^{w} - 1)G\}$
            \Ensure $kG$

            \State $Q \gets G$
            \For{$i$ from $l-1$ to $0$}
                \State $Q \gets 2\cdot Q$
                \If {$k_i \neq 0$}
                    \State $Q \gets Q + k_{i}G$
                \EndIf
            \EndFor
        \end{algorithmic}
    \end{algorithm}


From the Algorithm~\ref{alg:kg}, we can find that the if-then block (Line 4) is vulnerable to side channel attacks.
An attacker can use a spy process to monitor the conditional branches through side channels.
Then he can get a Double-Add chain, and determine  whether $k_i$ is zero or not based on this chain.
The attacker can  use this  information to recover the  private key.

In OpenSSL, the bit length of $k$ is set to a fixed value$\lfloor\log_{2}{q}\rfloor + 1$ of by adding itself with $q$
or $2q$, which can resist the remote timing side channel attack \cite{Brumley2011}.
In most cases, the multiplication is done as $(k + q)G$, but it is still vulnerable in lattice attacks \cite{Dahmun2016}.

Also, OpenSSL uses the modified wNAF representation instead of the generalized one stated in Algorithm~\ref{alg:wnaf} to avoid length expansion in some cases and to make more efficient exponentiation.
The representation of modified wNAF is very similar to the wNAF.
Each non-zero coefficient is followed by at least $w$ zero coefficients,
 except for the most significant digit which is allowed to violate this condition in some cases.
As the modification on wNAF has little affects on the attack results,
%the use of modified wNAF affects the attack results little,
 we only consider the case of the generalized wNAF for clarity. %最后一段需要修改，且这一节需要和多篇文章对比完善, 还有需要在合适的位置加上我们使用256的曲线，window 大小为3


%对其进行一些分析，有条件判断 可以通过侧信道获取信息。
%
%实际中的使用k+q
\subsection{The Scalar Multiplication in OpenSSL}
\label{intro_smulinssl}
In OpenSSL versions between 0.9.7 and 1.1.0h~\cite{openssl}, the scalar multiplication with wNAF representation is implemented in the function \verb+ec_wNAF_mul()+.
The core computation of the function is shown in Algorithm  \ref{alg:smopenssl}.

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\begin{algorithm}[t]
        \caption{The Implementation of The Scalar Multiplication in OpenSSL}
        \label{alg:smopenssl}
        \begin{algorithmic}[1]
            \Require Scalar $k$ in wNAF $\{k_0$, $k_1$, ..., $k_{l-1}\}$ and precomputed points $\{G, 3G, ..., (2^{w} - 1)G\}$
            \Ensure $kG$
			
			\State $r \gets 0$, $is\_neg \gets 0$, $r\_is\_inverted \gets 0$
            \For{$i$ from $l-1$ to $0$}
            	\If {$r \neq 0$}
            		\State \Call{$EC\_POINT\_dbl$}{$r$}     {    }  $//$ $double$
                \EndIf
                \If {$k_i \neq 0$}
                	\State $is\_neg \gets (k_i < 0)$
                	\If {$is\_neg$}
                		\State $k_i \gets -k_i$
                	\EndIf
                	\If {$is\_neg \neq r\_is\_inverted$}
                		\If {$r \neq 0$}
                			\State \Call{$EC\_POINT\_invert$}{$r$}   {    }  $//$ $invert$
                		\EndIf                	
                    	\State $r\_is\_inverted \gets !r\_is\_inverted$
                	\EndIf
                	\If {$r = 0$}
                		\State $r \gets $ \Call{$EC\_POINT\_copy$}{$k_{i}G$}
                	\Else
                		\State $r \gets $ \Call{$EC\_POINT\_add$}{$r, k_{i}G$} {   }  $//$   $add$
                	\EndIf
                \EndIf
            \EndFor
            \State \Return r
        \end{algorithmic}
\end{algorithm}

In this function, it iterates the $k$ from the most significant digit to the least significant digit in its wNAF representation.
 In each digit, it performs a double operation (the \verb+EC_POINT_dbl()+ function).
  If the digit is not zero, it runs into the if-then block in Line 6, and first determines whether an invert function is needed. % to execute.
   The invert function is to compute the inverse of a point (the internal value of $kG$ here).
If the sign of the non-zero digit $k_i$ is opposite to the previous  non-zero digit,
 the invert operation (\verb+EC_POINT_invert()+) is performed (Line 13),
which makes it only need to precompute and store the points $\{G, 3G, ..., (2^{w} - 1)G\}$, and saves a half of storage space.
Then, an addition operation (the \verb+EC_POINT_add()+ function) is invoked to add the internal value of $kG$  with  a precomputed point indexed by  the
absolute value of the digit.


From Algorithm \ref{alg:smopenssl}, it can be found that two conditional branches are vulnerable.
In each loop, the double operation is always performed.
But the add operation is only performed when the digit is not zero and the invert operation is only performed when the sign of the digit is opposite to previous one.
Therefore, if a spy process can obtain the execution sequence of
  the double and addition operations,
one can determine whether each digit of $k$ is zero or not according to this sequence.
Also,  the execution sequence of the invert operation can be used to determine the signs of the non-zero digits combining with the former sequence.



\subsection{Cache Side Channel Attacks}
\label{intro_cacheattack}
Cache side-channel attacks, firstly proposed in 2002~\cite{Page2002},  take advantage of the characteristic of cache activity
 that accessing data from caches is much faster than from memory.
Attackers exploit these time variations to deduce the operations of the target process and then infer the key information.

For the symmetric cryptography,
Tsunoo et al. \cite{Tsunoo2003Cryptanalysis} and Bernstein \cite{Bernstein2005Cache} proposed the first practical cache attacks on DES and AES, respectively.
 These methods statically analyze the relation between the overall execution time and lookup table indexes which are affected by the cache behavior.
Bonneau and Mironov \cite{Bonneau2006} showed how to exploit cache collisions to recover the  AES secret key.
In 2006, Osvik et al. \cite{Osvik2006} presented two access-driven attacks: Evict+Prime and Prime+Probe,
%Although the latter one proved to be significantly more efficient, both of them
to recover the AES encryption key used by an OpenSSL server.
 Ac{\i}i{\c{c}}mez et al.~\cite{ac2006} presented a trace-driven attack targeting AES that exploited the cache collision during the first round.
In 2011, Gullasch et al.~\cite{cachegame2011} first presented the access-driven attack on AES encryption by blocking the AES execution after each memory access using the process scheduling algorithm.
In 2014, Irazoqui \cite{Irazoqui2014} exploited the Flush+Reload technique to attack the AES.

For the asymmetric cryptography,
The works~\cite{Percival2005CACHEMF,Onur2007Yet} attacked RSA, by exploiting the data cache and the instruction cache respectively. % to obtain the leaked information.
Then
Brumley and Hakala \cite{Brumley2009} mounted an L1 data cache-timing attack to recover the 160-bit ECDSA private key by obtaining the LSBs of ECDSA ephemeral keys from the \verb+dgst+ tool in OpenSSL 0.9.8k.
 While Ac{\i}i{\c{c}}mez et al. \cite{Brumley2010} used an L1 instruction cache-timing attack to recover a 160-bit DSA private key in OpenSSL 0.9.8l from the same tool.
 In 2014 Yarom et al. proposed the Flush+Reload method using the L3 cache to attack RSA \cite{flushreload} and ECDSA~\cite{yarom2014recovering} private key.
Also, this method is improved to attack the ECDSA with wNAF representation in \cite{Benger2014,Van2015,Fan2016}.
%Benger et al.~\cite{Benger2014} and Van de Pol et al. \cite{Van2015} demonstrated the viability of the Flush+Reload technique to recover ECDSA encryption keys.
%Fan et al. \cite{Fan2016} proposed a new way of extracting and utilizing information from the Flush+Reload attack.
In 2006, the variants of Flush+Reload are presented such as Flush+Flush \cite{gruss2016flush} and Prime+Abort \cite{disselkoen2017prime+abort}.
They exploited different methods to observe the cache access patterns to recover the private key.
 %and could be used in both local and virtualized environments.

In cloud computing environment, various cache side channel attacks are also proposed.
In 2009, Ristenpart et al.~\cite{get-off-my-cloud} presented methods to co-locate two virtual machines (VMs) and successfully recovered keystrokes from the co-resident victim's VM by the cache side-channel attacks.
Based on this work~\cite{get-off-my-cloud}, various attacks are extended to the co-resident VMs.
%This work was the basis of the cache attacks cross VMs because the caches were only shared with co-resident VMs.
For instance, Flush+Reload was used to attack AES \cite{Irazoqui2014} and RSA\cite{flushreload} in the cross-VM scenario.
Also, the Prime+Probe method was
adapted to work in virtualized environments by Zhang et al.~\cite{YinqianZhang2012-cross-vm} and Liu~\cite{liu2015last} to recover ElGamal encryption keys.
Irazoqui et al.~\cite{fine2014} recovered AES keys in virtualized environments with Bernstein's attack.

%Many attack methods are proposed \cite{Bonneau2006, Bernstein2005Cache, Osvik2006, cachegame2011, flushreload}
% since it is demonstrated feasible in theory \cite{Page2002}.
Here, we provide the detailed processes of Flush+Reload \cite{flushreload} and Flush+Flush \cite{gruss2016flush},
 which can be used to monitor the execution sequence of functions in the implementation of ECDSA.
%在近些年的研究中，访问驱动的攻击受到研究者们的青睐，因为其具有更高的攻击精度，能够很准确的获取到目标进程对cache的访问情况，以及更广的使用场景，例如对虚拟化云环境进行攻击。接下来，我们对两种典型的访问驱动攻击进行介绍，这两种攻击和本文相关。

The Flush+Reload attack \cite{flushreload} employs a spy process to monitor whether the specific memory lines have been accessed or not by the victim process.
So this attack relies on shared memory between the spy and the victim processes.
For attacks in the same machine, the spy can map the victim program file, the victim data file or shared libraries into its own address space to share these pages with the victim.
While in the virtualization environments, the page de-duplication technique of the VMM ensures the page sharing between the spy and the victim.
%监控LLC，需要写一下
The execution of such an attack consists of three phases:
\begin{itemize}
  \item
    \textbf{Flush:}
    The attacker uses the \verb+clflush+ instruction to flush the desired memory lines out from the caches.
    This ensures that these lines are accessed from the memory instead of the caches for the next time.
  \item
    \textbf{Wait:}
    the attacker waits a moment while the victim is running.
  \item
    \textbf{Reload:}
    This phase detects whether the victim accesses the memory lines flushed in the first phase during the waiting time.
    The attacker accesses the desired memory lines to reload them into caches, and measures the time.
%From the reload time, the attacker determines whether the memory lines are accessed by the victim.
    The longer reload time means that the victim does not access the data and the attacker has to reload the data from the memory.
    Otherwise, it means that the victim accesses the data.
%    So these memory lines are accessed by the victim during the waiting time.%需要精简
\end{itemize}

The Flush+Flush attack \cite{gruss2016flush} also assumes the shared memory.
%Unlike measuring the reload time directly affected by the cache access,
It relies on the execution time of the \verb+clflush+ instruction,
  which is affected by whether the to-be-flushed data are cached or not.
The execution time of \verb+clflush+ is shorter if the data are not cached
 and longer if the data are cached.
So according to this time, the attackers determine the victim's cache activities.

In general, the Flush+Flush attack also consists of three phases.
The first two phases are the same as in the Flush+Reload attack.
But in the third phase, it flushes the cache again and measures the flush time instead of the reload time.
%As the third phase flushes the caches, it doubles as the first phase for subsequent observations.

%再一段F+F 和 F+R进行对比：更加高效，精度更高，F阶段可以当成是下一循环的F，
The execution time of \verb+clflush+ is less than the reload time on average,
    and the first and the third phase are merged together in the Flush+Flush attack.
  Therefore, the Flush+Flush attack runs in a higher frequency than the Flush+Reload attack.
%Thus, the Flush+Flush attack has a better accuracy.
%Furthermore, compared with the Flush+Reload attack,
%the Flush+Flush attack does not trigger prefetches when monitoring consecutive memory lines, otherwise, it may affect the validity of the attack.


%这一节要和多篇文章进行对比改进，f+r攻击需要精简。
%f+r的算法伪代码考虑需不需要添加。

\subsection{The Hidden Number Problem and Lattice Attack}
\label{intro_hnp}

For the wNAF algorithm,
 the if-then block (Line 4 in Algorithm~\ref{alg:kg}) is vulnerable to side channel attacks.
An attacker can use a spy process to monitor the conditional branches through side channels.
Then he can get a Double-Add chain, and determine whether  $k_i$ is zero or not from this chain.
But this is not enough to determine the complete ephemeral key,
 only some bits of the ephemeral key are obtained.
The attacker then use this extracted information to launch a lattice attack to recover the private key.


The Hidden Number Problem (HNP) is first presented by Boneh and Venkatesan~\cite{boneh1996} in 1996.
It is used to recover the secret key of Diffie-Hellman key exchange~\cite{boneh1996}, DSA~\cite{HG2001} and ECDSA~\cite{Nguyen2003}, given some leaked consecutive bits of the ephemeral key.
Given a prime number $q$ and a positive $l$,
 and let $t_1, t_2, ..., t_d$ be randomly chosen, which are uniformly and independently in $\mathbb{F}_q$.
The HNP can be stated as follows:
  recovering an unknown number $\alpha \in \mathbb{F}_q$ such that the known number pairs $(t_i, u_i)$ satisfy
  $$v_i = |\alpha t_i - u_i|_{q} \leq q/2^{l+1}, \ \ \ \ 1 \leq i \leq d,$$
   where $|\cdot|_q$ denotes the reduction modulo $q$ into range $[-q/2, ..., q/2)$.
If $|\alpha t - u|_{q} \leq q/2^{l+1}$ is satisfied,
the integer $u$ represents the $l$ most significant bits of $\alpha t$ which is defined as ${MSB}_l(\alpha t)$.


The Extended Hidden Number Problem (EHNP) introduced in~\cite{ehnp} is stated as follows, which also can be used to recover the ECDSA private key~\cite{Fan2016}.
Let $N$ be a prime number. Given $u$ congruences
$$
\beta_{i}x + \sum_{j=1}^{l_i}{a_{i,j}k_{i,j}} \equiv c_i \ \ \ \bmod N, \ \ \ 1 \leq i \leq u \ ,
$$
where $k_{i,j}$ and $x$ are unknown variables satisfying $0 \leq k_{i,j} \leq 2^{\varepsilon_{i,j}}$ and $0 < x < N, \beta_i, a_{i,j} , c_i, l_i \text{ and } \varepsilon_{i,j} $ are all known.
%The EHNP can be further converted to the approximate SVP in some suitable lattice to find the unknown $x$ (the hidden number) which satisfies the conditions above.
The EHNP is to find the unknown $x$ satisfying the conditions above.

For ECDSA algorithm, attackers take advantage of the equation $s = k^{-1} (h(m) + r\cdot\alpha) \bmod q$.
Based on the partial information about the ephemeral key obtained by the attackers through the cache side channels,
 they transform this equation to satisfy the form of HNP or EHNP.
   Then the private key as the hidden number can be recovered
      by solving the SVP/CVP problem in lattice converted from HNP or EHNP using the lattice reduction algorithm such as LLL \cite{Lenstra1982} or BKZ \cite{Schnorr1994}.

%we can use  algorithm to solve the SVP problem, while use Babai \cite{Babai1986} algorithm or Enumeration technique to solve the CVP problem.

%这一段说，用cache攻击可以获得信息，然后将其转化成hnp问题来求解。
%For the ECDSA algorithm implemented by OpenSSL with the wNAF,
%  the attackers can obtain some consecutive bit fragments of the ephemeral key $k$ through the cache side channels.
%Then, the problem of recovering the secret key can be transformed to the HNP problem.
% The attackers can recover the secret key by solving the HNP problem using lattice reduction algorithms.

%
%The HNP problem can be converted to the CVP/SVP problem in lattices
% and solved by the lattice reduction.
%Here we provide a brief introduction.
%For more details on lattice, please refer to the literature \cite{latticereduction2000}.
%Consider the Euclidean space $\mathbb{R}^{d}$
% and let $B = \{\mathbf{b_1}, \mathbf{b_2}, ..., \mathbf{b_z}\}$ be a set of linearly independent vectors in $\mathbb{R}^d$.
%The set of vectors
%$$
%L = L(B) = \{\sum_{i=1}^{z}{\beta_i\mathbf{b_i}} \  |\ \beta_i \in \mathbb{Z} \}
%$$
%is the lattice generated by $B$.
%The set $B$ is called a basis of $L$, and $L$ is spanned by $B$.
%The number $z$ representing the number of vectors in $B$ is the dimension or rank of $L(B)$.
%If $z = d$, the lattice $L(B)$ is a full-dimension lattice.
%As the lattice is a set of vectors,
%  the norm of the shortest non-zero vector is called the first minima and denoted by $\mathbf{\lambda_1}(L)$.
%That is, $\mathbf{\lambda_1}(L) = \min\{\|\mathbf{u}\| \ |\  0 \neq \mathbf{u} \in L\}$, where $\|\mathbf{u}\|$ denotes the Euclidean norm of the vector $\mathbf{u}$.
%The problem of finding a non-zero vector $\mathbf{v} \in L$ with the minimal norm is called the shortest vector problem (SVP).
% While for a lattice $L$ and an arbitrary vector $\mathbf{v} \in \mathbb{R}^d$,
% the problem of finding a lattice vector $\mathbf{u} \in L$ of minimal distance from $\mathbf{v}$ is called the closest vector problem (CVP) similarly.
%  In other words, finding a vector $\mathbf{u}$ satisfied $\|\mathbf{u}\| = \min\{\|\mathbf{u} - \mathbf{v}\| \ |\   \mathbf{u} \in L\}$.
%
%Exploiting lattices to solve the HNP problem, we construct a $d+1$ dimensional lattice $L(B)$ spanned by the rows of the following matrix:
%$$B =
%\left(
%  \begin{array}{ccccc}
%    q & 0 & \cdots & 0 & 0 \\
%    0 & q & \ddots & \vdots & \vdots \\
%    \vdots & \ddots & \ddots & 0 & \vdots \\
%    0 & \cdots & 0 & q & 0 \\
%    t_1 & \cdots & \cdots & t_d & 1/2^{l+1} \\
%  \end{array}
%\right).
%$$
%Considering the vector $\mathbf{h} = (\alpha t_1 \bmod q, ..., \alpha t_d \bmod q, \alpha /2^{l+1})$,
% it can be obtained by multiplying the last row vector of $B$ by $\alpha$ and then subtracting appropriate multiples of the first $d$ row vectors.
%Thus the vector $\mathbf{h}$ belongs to $L(B)$.
%We call $\mathbf{h}$ the hidden vector because the last coordinate of $\mathbf{h}$ discloses the hidden number $\alpha$.
%Let the vector $\mathbf{u} = (u_1, ..., u_d, 0)$,
% so the distance between $\mathbf{h}$ and $\mathbf{u}$ is $\|\mathbf{h} - \mathbf{u}\| \leq q\sqrt{d+1}/2^{l+1}$.
%Because the lattice determinant of $L(B)$ is $q^d/2^{l+1}$,
%  the vector $\mathbf{h}$ is very close to the vector $\mathbf{u}$.
%Solving the CVP problem with input $B$ and $\mathbf{u}$ reveals the vector $\mathbf{h}$,
% hence the private key $\alpha$ is recovered.
%
%Because solving the CVP instance requires exponential time in the lattice rank,
% we can use the embedding technique \cite{Nguyen1999} to transform it to an SVP instance which just requires the polynomial time to solve.
%We construct a $d+2$ dimensional lattice $L(B')$ spanned by the rows of the matrix
%$$B' =
%\left(
%  \begin{array}{cc}
%    B & 0 \\
%    \mathbf{u} & q/2^{l+1} \\
%  \end{array}
%\right).
%$$
%Similarly, the vector $\mathbf{h}' = (\alpha t_1 - u_1 \bmod q, ..., \alpha t_d - u_d \bmod q, \alpha /2^{l+1}, -q/2^{l+1})$ belongs to the lattice $L(B')$.
% Its norm satisfies that $\|\mathbf{h}'\| \leq q\sqrt{d+2}/2^{l+1}$,
%  while the lattice determinant of $L(B')$ is $q^{d+1}/2^{2l+2}$.
%   This indicates that the vector $\mathbf{h}'$ is a very short vector.
%Note that this lattice also contains another vector $(-t_1, ..., -t_d, q, 0)\cdot B = (0, ..., 0, q/2^{l+1}, 0)$,
% which is most likely the shortest vector of the lattice.
%So we expect the second vector in a reduced basis of the lattice is equal to $\mathbf{h}'$ with a ``good'' chance for a suitably strong lattice reduction algorithm.
%Then we can acquire the hidden number $\alpha$ by solving the SVP problem.


\subsection{Partial Nonce Disclosure Attacks on DSA/ECDSA}
Various works are proposed to exploit partial nonce disclosure to recover long-term private keys
 of the algorithms based on the discrete logarithm problem.
In this section, we provide a brief description of these works.
%They can be classified into (1) ones proving that exploiting the partial information can recover the whole private key,
% and (2) ones that focus on how to obtain the partial information and construct appropriate lattice attacks to recover the private key.
%Some of them focus on
%proving that exploiting the partial information can recover the whole private key.
% And others pay more attention on how to obtain the partial information and construct appropriate lattice attacks to recover the private key.

% first
Boneh and Venkatesan \cite{boneh1996} initially investigated to use the partial information of the ephemeral key to construct an HNP problem and recovered the private key of Diffie-Hellman by solving it using the lattice reduction algorithm.
 Howgrave-Graham and Smart \cite{HG2001} extended this work to recover the DSA private key by  constructing an HNP instance from leaked LSBs and MSBs of the ephemeral key.
  Nguyen and Shparlinski \cite{Nguyen2002} proved that
      knowing the $l \geq 3$ LSBs, the $l+1$ MSBs  or any $2l$ consecutive bits of a certain number of ephemeral keys was enough for recovering the DSA private key.
 They recovered  a $160$-bit DSA key only using the $3$ LSBs of a certain number of ephemeral keys.
 Further, they extended these results to ECDSA~\cite{Nguyen2003}.
Liu and Nguyen \cite{Liu2013} improved the results that only 2 LSBs were required for breaking a 160-bit DSA key.

%In 2014, Benger et al. \cite{Benger2014} extended the technique in \cite{Nguyen2002} to use a different length of leaked LSBs for each signature.
% They recovered the secret key of OpenSSL's ECDSA implementation for the curve secp256k1 using about $200$ signatures.
%Van de Pol et al. \cite{Van2015} exploited the property of the modulus in some elliptic curves so that they could use all of the information leaked in the top half of the ephemeral keys to construct the HNP instance, allowing them to recover the secret key after observing only $14$ signatures.
%Fan et al. \cite{Fan2016} transformed the problem of recovering the secret key to the extended hidden number problem (EHNP)
%  which was solved by the lattice reduction algorithm.
%   Then the number of signatures needed was reduced to $4$.

%second
Brumley and Hakala \cite{Brumley2009} used an L1 data cache-timing attack to recover the LSBs of ECDSA ephemeral keys in OpenSSL 0.9.8k.
 They recovered a 160-bit ECDSA private key using the attack in \cite{HG2001} with  $2,600$ signatures ($8K$ with noise).
Analogously, Ac{\i}i{\c{c}}mez et al. \cite{Brumley2010} used an L1 instruction cache-timing attack to recover the LSBs of DSA ephemeral keys in OpenSSL 0.9.8l.
 It required $2,400$ signatures ($17K$ with noise) to recover a 160-bit DSA private key.
 Besides, both attacks required HyperThreading architectures.
In 2011, Brumley and Tuveri \cite{Brumley2011} mounted a remote timing attack on the implementation of ECDSA with binary curves in OpenSSL 0.9.8o.
 They obtained the MSBs of the ephemeral keys through the timing attack and recovered the private key after collecting information over 8,000 TLS handshakes.
In 2013, Mulder et al. \cite{Mulder2013} took advantage of a template attack to recover some LSBs of the ephemeral key.
They improved the Bleichenbacher's FFT-based (Fast Fourier Transform) attack by using BKZ for range reduction to solve the HNP problem.
Their attack could extract the entire private key using a 5-bit leak of the ephemeral key from 4 000 signatures.
%Benger et al. \cite{Benger2014} and Van de Pol et al. \cite{Van2015} used the Flush+Reload technique to acquire the information of the ephemeral key.
In 2014, Benger et al. \cite{Benger2014} extended the technique in \cite{Nguyen2002} to use a different length of leaked LSBs for each signature.
 They recovered the secret key of OpenSSL's ECDSA implementation for the curve secp256k1 using about $200$ signatures.
Then in 2015,
Van de Pol et al. \cite{Van2015} exploited the property of the modulus in some elliptic curves so that they could use all of the information leaked in the top half of the ephemeral keys to construct the HNP instance, allowing them to recover the secret key after observing only $14$ signatures.
In 2016, Allan et al. \cite{Allan2016} improved the results in \cite{Van2015} by using a performance-degradation attack to amplify the side-channel. The amplification allowed them to recover a 256-bit private key in OpenSSL 1.0.2a after observing only 6 signatures.
Fan et al. \cite{Fan2016} transformed the problem of recovering the secret key to the extended hidden number problem (EHNP)
 which was solved by the lattice reduction algorithm.
  Then the number of signatures needed was reduced to $4$.
Genkin et al. \cite{Genkin2016} performed electromagnetic and power analysis attacks on mobile phones.
 They showed how to construct HNP triples when the signature uses the low $s$-value.
Pereida et al. \cite{Pereida2016} showed that the DSA implementation in OpenSSL is vulnerable to cache-timing attacks due to a programming error,
 and exploited the vulnerability to attack against SSH (via OpenSSH) and TLS (via stunnel).
In 2017, Wang et al. \cite{Wang2017} exploited the HNP to recover the private key for the 256-bit curve using $85$ signatures using a few information from the Flush+Reload attack.
 Zhang et al. \cite{Zhang2017} extended  the attack in ~\cite{Nguyen2003} to SM2 Digital Signature Algorithm (SM2-DSA), which is a Chinese version of ECDSA.




%1 什么是格

%2 什么是格困难问题

%3 HNP问题如何用格来求解


